Calculate FD

### 2020-06-25 analysis/calc_fd.Rmd
Calculate FD in chunks to reduce parallelization overhead

get_fd <- function(data, filter_plot){
  require(FD)

@@

  setwd(here::here())
  return(fd_out)
}

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup()# %>%
  #filter(!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

>>>>

get_fd <- function(obs_data, filter_plot){
  require(FD)

  data <- obs_data %>%
    filter(plot_id == filter_plot)

@@

  setwd(here::here())
  print(filter_plot)
  return(fd_out)
}

@@

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot)) %>% #remove unlabeled plots 
  group_by(plot_id, year) %>%
  filter(n_distinct(id) > 4) %>%
  group_by(plot_id) %>%
  filter(n_distinct(year) > 4) %>% 
  ungroup()# %>%
  #filter(!study_id %in% c(195, 360), #exclude because they break
         #!study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

The dataset is too big to copy to each parallel thread, so we split the dataset into chunks 
```{r}
#number of chunks to split original dataset into 
num_groups = 4

plot_sizes <- data %>%
  count(plot_id) %>%
  arrange(desc(n)) %>%
  mutate(group = rep_len(1:num_groups, dim(.)[1]))

get_parallel_FD <- function(data, group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- data %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- future_map_dfr(group_plots$plot_id, get_fd_safe, data = group_data)

  print(group_num)
  return(FD)
}

fd <- map_dfr(1:num_groups, get_parallel_FD, data = data)
```
